Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-07 sections/observations.tex
Added linear adjustment function to likear adjustment section.

%Image of Raw Data

@@

%%Image of linear adjustment functino being added to raw data?

@@

The first step in our data analysis is to correct for the tracking error.
We found average Analog to Digital Unit (ADU) counts for the duration of time after 4th contact and average ADU counts for the same duration of time before 1st contact.
We then created a linear function that shifts the data at the end of the lightcurve upward and decreases in effect to 0 at 1st contact.
%Image of smoothing being done to above image?

@@

%Image of normalization being done to above image?

>>>>

@@

@@

The first step in our data analysis is to correct for the tracking error caused by the gust of wind.
We assume that this tracking error caused the radio intensity to decrease linearly with time.
To create this error correction function, we found the slope between a point ~2 minutes before 1st contact and a point ~2 minutes after 4th contact. 
The sign was then flipped on the slope and combined with the x value of the point at 1st contact in point slope form in Equation \ref{linear_adjustment_function}.
This function is added to the lighturve to adjust for the tracking error.
\begin{equation}\label{linear_adjustment_function}
Y = 128.4(x-2460409.2318317825)
\end{equation}
Where $Y$ is the adjustment value and $X$ is the time coordinate of each data point. 

@@
